---
title: "vignette of hw2"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette of hw2}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


To download and install the package, use `devtools`:

```{r install_devtool, results = 'hide', message=FALSE}
library(devtools)
install_github("sdeng24/statscomputing")
```

You can subsequently load the package with the usual R commands:

```{r load, message=FALSE}
library(statscomputing)
```
## Solving Linear Equations

For a given matrix A and b, solve the euqation $Ax=b$ by Gauss-Seidel("G-S") or Jacobi iterative method..For Jacobi method, you can do parallel computing by choosing ncores.(However, it's not recommended since it takes much longer for the commuting of different cores. ) It returns the relative error at each iteration and the final solution. Below is an example from hw1.

```{r hw1.1}
A<-HWGen(100,3)
v<-rep(c(1,0),50)
b<-A%*%v
object1<-solve_ols(A,v,method="G-S")
object1$solution
```

## Leveraging Regression

Fitting a linear model with big data can be computationally expensive. Instead, we can use subsamples of the data to do the regression and still get a fairly good result. There can be different strategies for sampling. Here we consider uniform sampling and weighted sampling. Below is the example of hw2

```{r hw1.2}
n=500
x<-rt(500,df=6)
noise<-rnorm(500)
y<--x+noise
algo_leverage(y,x,r=100,method="weighted")
```

## Coordinate  Descent  for  Elastic  Net

The objective in the function is $$\frac{1}{2n}\sum_{i=1}^n (y_ i-x_i^T\beta)^2+\lambda\frac{(1-\alpha)}{2}||\beta||_2^2+\lambda ||\beta||_1$$. We can assume $\frac{1}{n}\sum_{i=1}^nx_{ij}^2=1$. Then the coordinate descent algorithm updates the j-th coordinate by $$\hat\beta_j^k \gets \frac{S_{\lambda\alpha}(\frac{1}{n}\sum_{i=1}^n x_{ij}(y_i-x_i^T\beta^{(k-1)})+\beta^{(k-1)}_j) }{1+\lambda(1-\alpha),}$$

where $S_{t}(x)$ is the softthresholding function $S_{t}(x)=\mathrm{sgn}(x)(|x|-\lambda)$.

Below is the exmple of hw1, and we can use "plot_el" to draw the solution path.
```{r hw1.3}
library(MASS)
n=50
p=20
beta<-c(2,0,-2,0,1,0,-1,0,rep(0,12))
sigma<-diag(rep(1,p))
sigma[c(1,2),c(2,1)]<-rep(0.8,2)
sigma[c(5,6),c(6,5)]<-rep(0.8,2)
X<-mvrnorm(n,rep(0,p),sigma)
Y<-X%*%beta+rnorm(n)

fit<-elnet_coord(X,Y,alpha=0.3)
plot_el(fit)
```


